Predicting Diabetes Based on Various Factors Using Machine Learning Models

### 2023-12-13 manuscript/manuscript.tex
Discussion advances

As this is a paper dealing with sensitive medical data, we have many limitations in order to be ethical as well as respecting patient 
privacy. Based on the data set collected we should be able to ensure patient privacy pretty well as names or any very unique identifiers 
are not listed with each entry. We simply have a ID and age for each entry so we do not have to worry as much for the sake of privacy. In 
terms of our direct models we may have to disregard some assumptions as they may not fit with real world data. If something unexpected 
happens we may have to reconsider the data set used and consider finding a new one. This will be done by a case by case scenario and will 
be investigated thoroughly before making any decisions.

>>>>

This study be expanded further by using other machine learning techniques to study the data, this can be used to cross-validate our results to ensure
that we are providing the most accurate information. Other machine learning techniques could include random forest and logistic regression, to give another
understanding of the data.

As this is a paper dealing with sensitive medical data, we have many limitations in order to be ethical as well as respecting patient 
privacy. Based on the data set collected we should be able to ensure patient privacy pretty well as names or any very unique identifiers 
are not listed with each entry. We simply have age for each entry so we do not have to worry as much for the sake of privacy as this cannot be traced
back to a particular person. In terms of our direct models we may have to disregard some assumptions as they may not fit with real world data. If something unexpected 
happens we may have to reconsider the data set used and consider finding a new one. This will be done by a case by case scenario and will 
be investigated thoroughly before making any decisions.
